District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-06-20 paper/paper.tex
Matt additions to supplementary figures: 1) Formatting improvements (need to convert this back to org) 2) Addition of technical appendix 3) In red, still to do

% Created 2023-05-30 Tue 07:57
% Intended LaTeX compiler: pdflatex
\documentclass[a4paper, 12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{color}
\usepackage{listings}
\usepackage{minted}
\usepackage{authblk}
\usepackage{breakcites}
\usepackage{apacite}
\usepackage[top=3cm, bottom=3cm, left=3cm, right=3cm]{geometry} % define (reduced) margin size
\usepackage[parfill]{parskip} % insert whitespace between new paragraphs
\setlength\parindent{0pt}
\tolerance=9999
\emergencystretch=10pt
\hyphenpenalty=10000
\exhyphenpenalty=100
\author[1]{Patrick O'Toole}
\author[1,2]{Matthew L. Thomas}
\author[1]{Oliver Stevens}
\author[1,3]{Kevin Lam}
\author[4]{Katherine Kripke}
\author[1]{Rachel Esra}
\author[5]{Ian Wanyeki}
\author[5]{Lycias Zembe}
\author[1]{Jeffrey W. Eaton}
\affil[1]{\emph{Imperial College London, London, United Kingdom}} \\
\affil[2]{\emph{Joint Centre for Excellence in Environmental Intelligence, University of Exeter and Met Office}} \\
\affil[3]{\emph{Department of Statistics, University of British Columbia}} \\
\affil[4]{\emph{Avenir Health, Takoma Park, MD, USA}} \\
\affil[5]{\emph{Joint United Nations Programme on HIV/AIDS (UNAIDS)}} \\
\date{17th October 2022}
\title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}
\begin{document}

@@

\begin{center}
\includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
\end{center}

\emph{Figure 1: Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type.}

>>>>

\documentclass{article}

\usepackage[top=3cm, bottom=3cm, left=3cm,right=3cm]{geometry}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{todonotes}
\usepackage{pdflscape}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{pdfpages}
\usepackage{setspace} 
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{float}
\usepackage{tikz}
\usepackage[colorlinks=true,citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{multirow}
\setlength{\tabcolsep}{5pt}
%%\setlength{\parindent}{0pt}
\usepackage[parfill]{parskip}
\renewcommand{\arraystretch}{1.5}

\renewcommand\Affilfont{\itshape\footnotesize}
\def\ci{\perp\!\!\!\perp}

\renewcommand\Affilfont{\itshape\footnotesize}
\linespread{1.5}

% \usepackage{lineno}
% \linenumbers

% Nature Bibliography style
\usepackage[backend=biber,style=nature]{biblatex}
\addbibresource{library.bib}

%%%%%%%%%%%%%
%%% Title %%%
%%%%%%%%%%%%%
\title{District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa}

\author{}
\date{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
    \centering
    % \includegraphics[width=.9\linewidth]{plots/01_survey_table.pdf}
    \caption{Household surveys detailing circumcision patterns in SSA. The colour and size of points are determined by the provider and sample size of each respective survey. Triangular points have no information on circumcision type.}
\end{figure}
